Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-04-04 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
updated paper version

Figure 1a shows the phantom used for a simulated image with dimensions of $250\times 250$ pixels to illustrate the differences between heterogeneous (dark, $\alpha=-2$) and homogeneous (light, $\alpha=-10$) regions, with $L = 5$. 
The areas are formed by independent draws from the $G^0_I$ distribution.

@@

We applied the proposed test statistics in actual SAR images acquired over cities, including Flevoland, Netherlands and Ottawa, Canada.   
These images were captured by the Sentinel-1A satellite operating in the C band,  with  VV polarization, intensity format, and $L=5$ nominal looks.
Both images have dimensions of $512 \times 512$ pixels and contain urban areas, water forest regions, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)-(b).

@@

```
```{r sim_SAR_Images_Frankfurt, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics, Frankfurt. (a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test; ',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_total_H.png")
knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_total_CV.png")
knitr::include_graphics("../Figures/PNG/Frankfurt_512_mnad_7_total.png")

```
```{r sim_SAR_Images_01Frankfurt, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of tests on simulated data with a threshold of $0.1$ of the $p$-value, Frankfurt. (a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_H_01.png")
knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_CV.png")
knitr::include_graphics("../Figures/PNG/Frankfurt_512_mnad_7_0.1.png")

@@

```{r sim_SAR_Images_Ottawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics, Ottawa. (a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test; ',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Ottawa_512_pvalue7x7_total_H.png")
knitr::include_graphics("../Figures/PNG/Ottawa_512_CV_pvalue7x7_total_CV.png")
knitr::include_graphics("../Figures/PNG/Ottawa_512_mnad_7_total.png")

```
```{r sim_SAR_Images_01_Ottawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of tests on simulated data with a threshold of $0.1$ of the $p$-value, Ottawa. (a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Ottawa_512_pvalue7x7_H_01.png")
knitr::include_graphics("../Figures/PNG/Ottawa_512_CV_pvalue7x7_CV.png")
knitr::include_graphics("../Figures/PNG/Ottawa_512_mnad_7_0.1.png")

>>>>

Figure&nbsp;\ref{fig:sim_SAR_Images}(a) shows the phantom used for a simulated image with dimensions of $250\times 250$ pixels to illustrate the differences between heterogeneous (dark, $\alpha=-2$) and homogeneous (light, $\alpha=-10$) regions, with $L = 5$. 
The areas are formed by independent draws from the $G^0_I$ distribution.

@@

We assessed the proposed test statistics using two real SAR images. For our analysis, we selected images of the city of Frankfurt, Germany, and Ottawa, Canada. 
These images were acquired by the Sentinel-1A satellite operating in the C band,  with  VV polarization, intensity format, and $L=5$ nominal looks.

Both images have dimensions of $512 \times 512$ pixels and contain urban areas, water and forest regions, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)-(b).

@@

```
```{r sim_SAR_Images_Frankfurt, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics in Frankfurt image. (a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test. ',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_total_H.png")
knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_total_CV.png")
knitr::include_graphics("../Figures/PNG/Frankfurt_512_mnad_7_total.png")

```
```{r sim_SAR_Images_01Frankfurt, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Test results with a threshold of $0.1$ of the $p$-value for the Frankfurt image. (a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_H_01.png")
knitr::include_graphics("../Figures/PNG/Frankfurt_512_pvalue7x7_CV.png")
knitr::include_graphics("../Figures/PNG/Frankfurt_512_mnad_7_0.1.png")

@@

```{r sim_SAR_Images_Ottawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistics in Ottawa image. (a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Ottawa_512_pvalue7x7_total_H.png")
knitr::include_graphics("../Figures/PNG/Ottawa_512_CV_pvalue7x7_total_CV.png")
knitr::include_graphics("../Figures/PNG/Ottawa_512_mnad_7_total.png")

```
```{r sim_SAR_Images_01_Ottawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Test results with a threshold of $0.1$ of the $p$-value for the Ottawa image. (a) Entropy-based test; (b) CV test; (c) $\\text{CV}_{\\text{MnAD}}$ test.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("40mm", "40mm","40mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Ottawa_512_pvalue7x7_H_01.png")
knitr::include_graphics("../Figures/PNG/Ottawa_512_CV_pvalue7x7_CV.png")
knitr::include_graphics("../Figures/PNG/Ottawa_512_mnad_7_0.1.png")

### 2024-04-04 Text/Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics.tex
updated paper version

Figure 1a shows the phantom used for a simulated image with dimensions
of \(250\times 250\) pixels to illustrate the differences between
heterogeneous (dark, \(\alpha=-2\)) and homogeneous (light,
\(\alpha=-10\)) regions, with \(L = 5\). The areas are formed by
independent draws from the \(G^0_I\) distribution.

@@

We applied the proposed test statistics in actual SAR images acquired
over cities, including Flevoland, Netherlands and Ottawa, Canada.\\
These images were captured by the Sentinel-1A satellite operating in the
C band, with VV polarization, intensity format, and \(L=5\) nominal
looks. Both images have dimensions of \(512 \times 512\) pixels and
contain urban areas, water forest regions, as shown in
Figures~\ref{fig:real_SAR_Images_coe}(a)-(b).

@@

\caption{Results of applying the test statistics, Frankfurt. (a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\text{CV}_{\text{MnAD}}$ test; }\label{fig:sim_SAR_Images_Frankfurt}
\end{figure}
\begin{figure}[H]

@@

\caption{Results of tests on simulated data with a threshold of $0.1$ of the $p$-value, Frankfurt. (a) Entropy-based test; (b) CV test; (c) $\text{CV}_{\text{MnAD}}$ test.}\label{fig:sim_SAR_Images_01Frankfurt}
\end{figure}

@@

\caption{Results of applying the test statistics, Ottawa. (a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\text{CV}_{\text{MnAD}}$ test; }\label{fig:sim_SAR_Images_Ottawa}
\end{figure}
\begin{figure}[H]

@@

\caption{Results of tests on simulated data with a threshold of $0.1$ of the $p$-value, Ottawa. (a) Entropy-based test; (b) CV test; (c) $\text{CV}_{\text{MnAD}}$ test.}\label{fig:sim_SAR_Images_01_Ottawa}
\end{figure}

>>>>

Figure~\ref{fig:sim_SAR_Images}(a) shows the phantom used for a
simulated image with dimensions of \(250\times 250\) pixels to
illustrate the differences between heterogeneous (dark, \(\alpha=-2\))
and homogeneous (light, \(\alpha=-10\)) regions, with \(L = 5\). The
areas are formed by independent draws from the \(G^0_I\) distribution.

@@

We assessed the proposed test statistics using two real SAR images. For
our analysis, we selected images of the city of Frankfurt, Germany, and
Ottawa, Canada. These images were acquired by the Sentinel-1A satellite
operating in the C band, with VV polarization, intensity format, and
\(L=5\) nominal looks.

Both images have dimensions of \(512 \times 512\) pixels and contain
urban areas, water and forest regions, as shown in
Figures~\ref{fig:real_SAR_Images_coe}(a)-(b).

@@

\caption{Results of applying the test statistics in Frankfurt image. (a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\text{CV}_{\text{MnAD}}$ test. }\label{fig:sim_SAR_Images_Frankfurt}
\end{figure}
\begin{figure}[H]

@@

\caption{Test results with a threshold of $0.1$ of the $p$-value for the Frankfurt image. (a) Entropy-based test; (b) CV test; (c) $\text{CV}_{\text{MnAD}}$ test.}\label{fig:sim_SAR_Images_01Frankfurt}
\end{figure}

@@

\caption{Results of applying the test statistics in Ottawa image. (a) $P$-values from the entropy-based test; (b) $P$-values from the CV test; (c) $P$-values from the   $\text{CV}_{\text{MnAD}}$ test.}\label{fig:sim_SAR_Images_Ottawa}
\end{figure}
\begin{figure}[H]

@@

\caption{Test results with a threshold of $0.1$ of the $p$-value for the Ottawa image. (a) Entropy-based test; (b) CV test; (c) $\text{CV}_{\text{MnAD}}$ test.}\label{fig:sim_SAR_Images_01_Ottawa}
\end{figure}
